### 2017-12-19 Paper/DGSM_PCE_MD_paper.tex
separate background section
separate space for abstract

\input{cover}

@@

\input{intro}

\section{Background}
\subsection{DGSM}
\[ 
    \mu_i = E\left(\left( \frac{\partial \mathcal{G}}{\partial \theta_i}\right)^2\right)
          \approx \hat\mu_i := \frac1N\sum_{j = 1}^N 
                  \left(\frac{\partial \mathcal{G}(x_j)}{\partial \theta_i}\right)^2
\]
Can consider variance of $\hat\mu_i$.

\subsection{Polynomial chaos}
\section{Method}

\section{Motivating examples}
\subsection{Borehole: Screening, Convergence, Verification}
\subsection{Semilinear elliptic PDE: Screening, Convergence, Verification}
\subsection{Nonlinear Oscillator: Screening, Convergence, Verification}

\section{Application: Phonon Transport in a Si bar}

Seven uncertain parameters; well-established nominal values exist;
\[
   \theta_i \sim U(\bar\theta_i - \epsilon_i, \bar\theta_i + \epsilon_i), 
   \quad \epsilon_i = 0.1 \bar\theta_i. 
\]
\begin{enumerate}
\item Include all details pertaining to the MD simulation: system, simulation, 
ensembles, etc. 
\item Results
\end{enumerate}

\section{Discussion}
\begin{enumerate}
\item Methodology is agnostic to the choice of surrogate.
\item As required for a PCE, the uncertain parameters need not be independent. 
\item Strategy depends on the application - methodology could be implemented 
sequentially or adaptively. 
\end{enumerate}

>>>>

\thispagestyle{empty}
\input{cover}

\baselineskip=22pt

@@

\input{abstract}
\clearpage

\input{intro}
\bigskip
\bigskip

\input{bg}
\bigskip
\bigskip

\input{method}
\bigskip
\bigskip

\input{examples}
\bigskip
\bigskip

\input{app}
\bigskip
\bigskip

\input{disc}
\bigskip
\bigskip

\input{ack}
\bigskip
\bigskip

\bibliographystyle{unsrt}
\bibliography{REFER}

\clearpage

\input{figures}
